Overcoming Hurdles to Green Living: Insights for Community Climate Action

### 2024-11-26 paper/paper.qmd
checking if correctly cleaned summary data 2021

>>>>

the following categories were not options under reasons unlikely to perform action   "Use public transit more",
  "Cycle more",
  "Walk more",
  "Purchase electric/hybrid vehicle in next 1-3 years",
  but they were categories for which actions are you most likely to take part in to address climate change.

no indiivdual data for 2021, used summary statistics instead
